A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-10-12 main.tex
5 edits

In this work, we have reviewed the concept of population stratification and explicitly defined an environmental mechanism by which it may confound the genotype-phenotype relationship \pb{not sure what this sentence means; what are you referring to?}. We have provided a broad outline of existing methods for ameliorating the effects of these unobserved confounding influences. In addition, we have provided a thorough review of two popular approaches for correcting for population structure in genetic data: PC-Lasso and LMM-Lasso. \pb{emphasize the \emph{penalized} nature of our work here, which is I think what makes it novel}

>>>>

In this work, we have reviewed the concept of population structure in a framework which \anna{formally differentiates between effects of population structure and those of the environment}. We have provided a broad outline of existing methods for ameliorating the effects of these unobserved confounding influences. In addition, we have provided a thorough review of two popular approaches for correcting for population structure in genetic data, \anna{now applied within a novel penalized framework}: PC-Lasso and LMM-Lasso.
